Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-11-20 ms.tex
better LS periodogram to show 1/f noise

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pixeltime_series_amp_0_full_fft_cleaned_True.pdf}
\caption{The discreet Fourier transform of the entire time series from one amplifier shows 1/f noise at low frequencies that levels off at high frequencies.
}\label{fig:pixelTSeriesFFT}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{avg_psd_amp_0.pdf}
\caption{The average Lomb Scargle periodogram from Amplifier 0's time series over 108 groups.
The line shows a 1/f slope law.
}\label{fig:pixelTSeriesFFT}
\end{figure*}
